{\steve}: A hierarchical Bayesian model for Supernova Cosmology

### 2019-02-05 papers/methods/paper.tex
Updating figure again

 \begin{figure}
 	\begin{center}
 		\includegraphics[width=\columnwidth]{tikz-figure0.pdf}
 	\end{center}
 	\caption{Probabilistic graphical model for our likelihood \added{without selection effects}. Double-lined nodes represent observed variables, diamond nodes represent deterministic variables, single-lined ellipse nodes represent fit variables. The SN box represents observed variables and latent variables for each individual supernova, whilst the survey box represents survey-specific variables, which in general describe the supernova population for the survey and the systematics associated with it. Variables that appear outside both boxes represent top level model parameters. \added{We note that we have shown the model to have latent variables $\lbrace M_B,\,x_1\,c\rbrace$, which uniquely determines $m_B$, given $\mu$ and other parameters. Thus, the two nodes $M_B$ and $m_B$, make up a single layer in our hierarchy, not two layers. In the code implementation, $m_B$ is more efficiently parametrised instead of $M_B$, however the mathematics remains constant regardless of if you parametrise $M_B$ or $m_B$ as one can determine the other. Finally, as we take redshift measurement $\hat{z}$, mass probability $\hat{m}$ and classification probability $\hat{p}$ as exact they are not conditioned on underlying distributions and are top level parameters. We add the deterministic $m$ and $p$ nodes in our diagram for clarity, however as they have a one-to-one mapping onto $\hat{m}$ and $\hat{p}$ respectively we simply use the observed values in the mathematics of the rest of the paper.}}
 	\label{fig:pgm}
 \end{figure}

@@

\begin{align}
&P({\rm data}|\theta) = \notag \\
&\int\, d\mu\, d\eta\, dz \ P( \hat{\eta}, \hat{\mathcal{C}}_\eta^{-1} | \eta, \delta \mathcal{Z}_i, \kappa_0, \kappa_1) P(\hat{z}|z) \notag \\
& P(\eta, \hat{m}, \hat{p} | \langle M_B \rangle, \langle x_1^i \rangle, \langle c^i \rangle, \mu, \delta(0), \delta(\infty), \sigma_{M_B}, \sigma_{x_1}, \sigma_c, \alpha, \beta) \notag \\
& P(\mu |z, \Omega_m, w) 
\end{align}

>>>>

 \begin{figure}
 	\begin{center}
 		\includegraphics[width=\columnwidth]{tikz-figure0.pdf}
 	\end{center}
 	\caption{Probabilistic graphical model for our likelihood \added{without selection effects}. Double-lined nodes represent observed variables, diamond nodes represent deterministic variables, single-lined ellipse nodes represent fit variables. The SN box represents observed variables and latent variables for each individual supernova, whilst the survey box represents survey-specific variables, which in general describe the supernova population for the survey and the systematics associated with it. Variables that appear outside both boxes represent top level model parameters. \added{We note that we have shown the model to have latent variables $\lbrace M_B,\,x_1\,c\rbrace$, which uniquely determines $m_B$, given $\mu$ and other parameters. Thus, the two nodes $M_B$ and $m_B$, make up a single layer in our hierarchy, not two layers. In the code implementation, $m_B$ is more efficiently parametrised instead of $M_B$, however the mathematics remains constant regardless of if you parametrise $M_B$ or $m_B$ as one can determine the other. We write out ${\rm mass}$ instead of $m$ to reduce possible confusion with magnitude in the diagram. Finally, as we take redshift measurement $\hat{z}$, mass probability $\hat{{\rm mass}}$ and classification probability $\hat{p}$ as exact they are not conditioned on underlying distributions and are top level parameters. We add the deterministic $m$ and $p$ nodes in our diagram for clarity, however as they have a one-to-one mapping onto $\hat{{\rm mass}}$ and $\hat{p}$ respectively we simply use the observed values in the mathematics of the rest of the paper.}}
 	\label{fig:pgm}
 \end{figure}

@@

\begin{align}
&P({\rm data}|\theta) = \notag \\
&\int\, d\mu\, d\eta\, dz \ P( \hat{\eta}, \hat{\mathcal{C}}_\eta^{-1} | \eta, \delta \mathcal{Z}_i, \kappa_0, \kappa_1) P(\hat{z}|z) \notag \\
& P(\eta, \hat{m}, \hat{p} | \langle M_B \rangle, \langle x_1^i \rangle, \langle c^i \rangle, \mu, \delta(0), \delta(\infty), \sigma_{M_B}, \sigma_{x_1}, \sigma_c, \alpha, \beta, z) \notag \\
& P(\mu |z, \Omega_m, w) 
\end{align}
